Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-05-04 revision-1/model.tex
checkpoint
first folder commit

@@

Given inputs $\store$ and ideal
functionality output $v$, we write $ \prob(\SIM(\store,v) = \store') $
to denote the probability that $\SIM(\store,v)$ returns corrupt views
$\store'$ as a result. We can then define the probability distribution
of corrupt views reconstructed by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\dist(\SIM(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \dist(\SIM(\store,v))(\store')\ \defeq\ \prob(\SIM(\store,v) = \store') 
  $$
\end{definition}
Then we can define passive security in the real/ideal
model as follows. 
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\views(\prog) = V$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM$ such that:
  $$
  \dist(\SIM(\store_{C},\idealf(\store))) = \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{definition}
Observe that this definition relies on protocol correctness, which
we can define as follows.
\begin{definition}[Passive Correctness]
  Given $\prog$ with output variables $\out{1},\ldots,\out{n}$ and ideal
  functionality $\idealf$, we say that $\prog$ is \emph{passive correct}
  for $\idealf$ iff for all $\store \in \mems(\secrets(\prog))$
  with $\idealf(\store) = v_1,\ldots,v_n$ we have
  $\progtt(\prog)(\out{1} \mapsto v_1,\ldots,\out{n} \mapsto v_n \mid \store) = 1$.
\end{definition}

@@

$$
\begin{array}{rclr}
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\store,\be}{\cid_2}}, \prog) & \cid_2 \in H\\
  (\store, \eassign{\mesg{w}}{\cid_1}{\be}{\cid_2};\prog) &\aredx&
  (\extend{\store}{\mesg{w}_{\cid_1}}{\lcod{\arewrite(\store_C,\be)}{\cid_2}}, \prog) & \cid_2 \in C
\end{array}
$$

$$
\dist(\SIM(\store_{S_H})) = \condd{\progtt(\prog)}{\houtputs \cup O_H}{\store_{S_H}}
$$

>>>>

We also define the \emph{support} of a distribution in the usual manner-
it is the set of values a set of variables can take on with non-zero
probability.
\begin{definition}[Support]
  $\support(\pmf) \defeq \{ (v_1,\ldots,v_n) \mid
  \pmf(x_1 \mapsto v_1, \ldots, x_n \mapsto v_n) > 0 \} $
\end{definition}

@@

Given inputs $\store$ and ideal
functionality output $v$, we write $ \prob(\SIM(\store,v) = \store') $
to denote the probability that $\SIM(\store,v)$ returns corrupt views
$\store'$ as a result. We can then define the probability distribution
of corrupt views reconstructed by the simulator as follows:
\begin{definition}
  Given $\store$, and $v$, we write $\dist(\SIM(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \dist(\SIM(\store,v))(\store')\ \defeq\ \prob(\SIM(\store,v) = \store') 
  $$
\end{definition}
Then we can define passive security in the real/ideal
model as follows. 
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\views(\prog) = V$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM$ such that:
  $$
  \dist(\SIM(\store_{C},\idealf(\store))) = \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{definition}
Observe that this definition relies on protocol correctness, which
we can define as follows.
\begin{definition}[Passive Correctness]
  Given $\prog$ with output variables $\out{1},\ldots,\out{n}$ and ideal
  functionality $\idealf$, we say that $\prog$ is \emph{passive correct}
  for $\idealf$ iff for all $\store \in \mems(\secrets(\prog))$
  with $\idealf(\store) = v_1,\ldots,v_n$ we have
  $\progtt(\prog)(\out{1} \mapsto v_1,\ldots,\out{n} \mapsto v_n \mid \store) = 1$.
\end{definition}

@@

In the malicious model we assume that corrupt clients are in the thrall of an
adversary $\adversary$ who does not necessarily follow the rules of the protocol.
We model this by positing a $\arewrite$ function which is given a corrupt memory
$\store_C$ and expression $\be$, and returns a rewritten expression that can
be interpreted to yield a corrupt input. Then we define an evaluation
relation that incorporates the adversary:
$$
\begin{array}{rclr}
  (\store, \xassign{x}{\be}{\cid};\prog) &\aredx&
  (\extend{\store}{x}{\lcod{\store,\be}{\cid}}, \prog) & \cid \in H\\
  (\store, \xassign{x}{\be}{\cid};\prog) &\aredx&
  (\extend{\store}{x}{\lcod{\arewrite(\store_C,\be)}{\cid}}, \prog) & \cid \in C
\end{array}
$$

$$
\begin{array}{rcl@{\qquad}r}
  (\store,\elab{\assert{\phi(\be)}}{\cid};\prog) &\redx& (\store,\prog) & \text{if\ } \phi(\lcod{\store,\be}{\cid}) \text{\ or\ } \cid \in C\\
  (\store,\elab{\assert{\phi(\be)}}{\cid};\prog) &\redx& (\store,\bot)  & \text{if\ } \neg\phi(\store,\lcod{\store,\be}{\cid})
\end{array}
$$

Given this we define the $\adversary$ distribution of $\prog$. 
\begin{definition}
  \label{def-progd}
  \label{definition-progd}
  Given program $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$, and
  any assumed pre-processing predicate $\preproc$ on memories, define:
  $$
  \aruns(\prog) \defeq \{ \store \mid \preproc(\store)  \wedge
  ((\store_{S\cup R},\prog) \aredx^* (\store,\varnothing) \vee (\store_{S \cup R},\prog) \aredx^* (\store,\bot)) \}
  $$
  and also define:
  $$
  \botruns(\prog) \defeq \{ \store\{ x_1 \mapsto \bot, \ldots, x_n \mapsto \bot \} \mid
  \store \in \aruns(\prog) \wedge \{ x_1,\ldots,x_n\} = (V \cup O) - \dom(\store) \}
  $$
  Then the \emph{$\adversary$ distribution of $\prog$}, written $\progtt(\prog,\adversary)$, is
  defined such that for all $\store \in \mems(\iov(\prog) \cup R)$:
  $$
  \progtt(\prog,\adversary) =  1 / |\botruns(\prog)| \ \text{if}\ \store \in \botruns(\prog), \text{otherwise}\ 0
  $$
\end{definition}

\begin{definition}[Malicious Simulation]
  Given a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$, honest and corrupt 
  clients $H$ and $C$, adversary $\adversary$, and honest inputs
  $\store \in \mems(S_H)$, the \emph{malicious simulation}  $\SIM(\store)$ has three phases:
  \begin{enumerate}
  \item In the first phase $\SIM_1$, $\adversary$ gives the
    simulator some $\store' \in \mems(S_C)$, and the simulator consults an
    oracle to compute $\idealf(\store \cup \store') \in \mems(O)$.
  \item In the second phase $\SIM_2$, the simulator is given the corrupt
    outputs $\idealf(\store \cup \store')_C$, which are again given to
    $\adversary$, who decides either to abort or not. If so, then the
    simulator is given $\sigma_{\mathit{out}} \defeq \{ \out{\cid} \mapsto \bot \mid \cid \in H \}$
    and arbitrary internal state $\Sigma$.
    Otherwise the simulator is given $\sigma_{\mathit{out}} \defeq \idealf(\store \cup \store')_H$
    and $\Sigma$.
  \item In the third phase $\SIM_3$, given $\store_{\mathit{out}}$ and $\Sigma$, the simulator
    finally outputs
    $\store_{\mathit{out}} \cup \store_{\mathit{views}}$ for some
    calculated $\store_{\mathit{views}} \in \mems(\houtputs)$.
  \end{enumerate}
\end{definition}

\begin{definition}[Malicious Security]
  We write $\dist(\SIM(\store))$ to
  denote the distribution of honest outputs and corrupt views reconstructed by the
  malicious simulation, where for
  all $\store'$:
  $$
  \dist(\SIM(\store))(\store')\ \defeq\ \prob(\SIM(\store) = \store') 
  $$
  Then a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is \emph{malicious
  secure} iff for all $H$, $C$, $\adversary$, and $\store \in \mems(S_H)$:
  $$
  \dist(\SIM(\store)) = \condd{\progtt(\prog,\adversary)}{\houtputs \cup O_H}{\store}
  $$  
\end{definition}
